Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
bandwidth before instances

\section{Experimental Validation}
\label{sec:expe}
In this section, we describe a series of numerical experiments to confirm 
the performance predictions of Section~\ref{sec:model}. To better
understand our results, we first perform some bandwidth measurements, followed
by the actual SpMV.

@@

\begin{figure*}
\centering
%
 \subfigure[On MIC with 240 threads, 64-byte memory
   alignment.]{\includegraphics[width=.40\linewidth]{figures/bandwidth_read_write.pdf}\label{fig:band_rw_MIC}}
%
  \hspace{.3in}
%
  \subfigure[On CPU with 32 threads, 32-byte memory
    alignment.]{\includegraphics[width=.40\linewidth]{figures/host_test1_readwrite_no_temporal_hint.pdf}\label{fig:band_rw_CPU}}

  \caption{Bandwidth performance on the host under idealized
    conditions as a function of matrix row size.  Entries with "cpp"
    denote cases where coding was performed without MIC vector
    intructions.  \todo{Can we label the x-axis "number of floats" or
      "size in MB"?}\todo{Can we use the same symbols in both charts?}
    \todo{Can we change the color scheme? in (a), I do not see the
      difference between "read\_cpp" and "read/write cpp"} }
  \label{fig:bandwidth}
\end{figure*}

>>>>

\section{Experimental Validation}
\label{sec:expe}
In this section, we describe a series of numerical experiments to
confirm the performance predictions of Section~\ref{sec:model}. To
better understand our results, we first perform some bandwidth
measurements, followed by the actual SpMV computations.

@@

\begin{figure*}[bth]
  \centering
  \subfigure[On MIC with 240 threads, 64-byte memory
    alignment.]{\includegraphics[width=.40\linewidth]{figures/bandwidth_read_write.pdf}\label{fig:band_rw_MIC}}
  %
  \subfigure[On CPU with 32 threads, 32-byte memory
    alignment.]{\includegraphics[width=.40\linewidth]{figures/host_test1_readwrite_no_temporal_hint.pdf}\label{fig:band_rw_CPU}}

  \caption{Bandwidth performance on the host under idealized
    conditions as a function of matrix row size.  Entries with "cpp"
    denote cases where coding was performed without MIC vector
    instructions.  \todo{Can we label the x-axis "number of floats" or
      "size in MB"?}\todo{Can we use the same symbols in both charts?}
    \todo{Can we change the color scheme? in (a), I do not see the
      difference between "read\_cpp" and "read/write cpp"} }
  \label{fig:bandwidth}
\end{figure*}
